### 2018-10-18 Sections/cloud_quantum_computing.tex
Minor, refs

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{modules_physical}
	\captionspacefig \caption{A possible physical realisation of commercially produced quantum modules, forming a \mbox{$2\times 3$} patchwork of cluster states. Each hosts a relatively small number of qubits. The nodes each have four optical interconnects, which are used to connect the modules via optical fibre. Entangling operations performed on photons shared via the interconnects create inter-module entanglement, yielding a distributed virtual quantum computer with far more qubits.}\label{fig:modules_physical}
\end{figure}

@@

Thus far we have focussed on computation as the key utility for outsourced quantum technologies, and certainly this is likely to be the dominant driving force behind quantum outsourcing\index{Outsourced quantum technology}. But of course not everyone wants to only solve complex algorithmic problems. Others may wish to study quantum systems themselves from the perspective of basic science research\index{Basic science research}.

@@

The availability of a globe-spanning quantum network on satellites brings the opportunity for fundamental quantum mechanical experiments and unprecedented length scales and velocities in the future. Satellite-to-satellite\index{Satellite-to-satellite communication} photon transfer can allow for ultra-long distance quantum communications that are not possible on Earth due to atmospheric loss. Another unique aspect of space is that satellites move at high velocities -- typically at $10^{-5} $ times the speed of light\index{Speed of light} for LEO satellites. The combination of both of these effects gives a unique opportunity for performing relativistic quantum information\index{Relativistic quantum information} experiments to test fundamental physics.

We anticipate that some of the first experiments will be extensions of what are already performed on Earth. For example, one can perform increasingly long space-based Bell violation tests\index{Bell inequality} at unprecedented distances \cite{bib:yin2017satellite}. Another possibility is to examine the speed of influence of entanglement, which bound the speed of entanglement \cite{bib:yin2013lower}. In space, such experiments could be extended much further, giving tighter bounds. There are demanding technical hurdles that must be overcome to succeed at such experiments, such as the necessity for synchronised clocks (Sec.~\ref{sec:clocks}).

 In addition to examining extensions of existing experiments, the high satellite velocities can be used to perform relativistic quantum information experiments, such as entanglement tests in the presence of special\index{Special relativity} and general relativity\index{General relativity}, Wheeler's delayed choice experiment\index{Wheeler's delayed choice experiment}, and enhanced quantum metrology \cite{sec:kaltenbaek2003proof, sec:scheidl2013quantum, sec:ahmadi2014relativistic}.

@@

Examples of how this type of model might be applied could include, but not be limited to research into:
\begin{itemize}
	\item Quantum information processing protocols, beyond only quantum computation, bits and qubits.
	\item Bose-Einstein condensates (BECs)\index{Bose-Einstein condensates (BECs)}.
	\item Light-matter interactions.\index{Light-matter interactions}
	\item Quantum thermodynamics and quantum statistical mechanics.\index{Quantum thermodynamics}\index{Quantum statistical mechanics}
	\item Quantum phase-transitions.\index{Quantum phase-transitions}
	\item Quantum optics, involving all manner of quantum states of light, beyond only those raised in Sec.~\ref{sec:opt_enc_of_qi}.\index{Quantum optics}
	\item Optical interferometry.\index{Optical interferometry}
	\item Providing a practical platform for university teaching.
\end{itemize}

In some instances, such outsourced quantum protocols might be applicable to encryption protocols, like those discussed in the next section, Sec.~\ref{sec:homo_blind}, enabling highly valuable secrecy for the experiments being conducted by researchers and their hard-earned results\footnote{Note, however, that the upcoming protocols are designed for application to particular optical states and protocols, and encryption schemes involving more generic quantum assets are likely to require some rethinking and adaptation (if possible at all, which isn't guaranteed!).}.

>>>>

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{modules_physical}
	\captionspacefig \caption{A possible physical realisation of commercially produced quantum modules\index{Node-X}, forming a \mbox{$2\times 3$} patchwork of cluster states. Each hosts a relatively small number of qubits. The nodes each have four optical interconnects, which are used to connect the modules via optical fibre. Entangling operations performed on photons shared via the interconnects create inter-module entanglement links, yielding a distributed virtual quantum computer with far more qubits. The computation is truly distributed and cooperative, in the sense that the entire computation is non-local, instead being collectively distributed across all the nodes, which coordinate their local operations via only classical communication. An alternate implementation is to replace the inter-node quantum links with Bell-pair distributers. Then entanglement swapping can be employed to swap the entanglement into a link between nodes.}\label{fig:modules_physical}
\end{figure}

@@

Thus far we have focussed on computation as the key utility for outsourced quantum technologies, and certainly this is likely to be the dominant driving force behind quantum outsourcing\index{Outsourced quantum technology}. But of course not everyone wants to only solve complex algorithmic problems. Others may wish to study quantum systems themselves from the perspective of basic science research\index{Basic science research}, or perform precise quantum metrology.

@@

The availability of a globe-spanning quantum satellite network brings the opportunity for fundamental quantum mechanical experiments and unprecedented length scales and velocities in the future. Satellite-to-satellite\index{Satellite-to-satellite communication} photon transfer can allow for ultra-long distance quantum communications that are not possible on Earth due to atmospheric loss. Another unique aspect of space is that satellites move at high velocities -- typically at $10^{-5} $ times the speed of light\index{Speed of light} for LEO satellites. The combination of both of these effects gives a unique opportunity for performing relativistic quantum information\index{Relativistic quantum information} experiments to test fundamental physics.

We anticipate that some of the first experiments will be extensions of what are already performed on Earth. For example, one can perform increasingly long space-based Bell violation tests\index{Bell inequality} at unprecedented distances \cite{bib:yin2017satellite}. Another possibility is to examine the speed of influence of entanglement \cite{bib:yin2013lower}. In space, such experiments could be extended much further, giving tighter bounds. There are demanding technical hurdles that must be overcome to succeed at such experiments, such as the necessity for synchronised clocks (Sec.~\ref{sec:clock_sync}).

 In addition to examining extensions of existing experiments, the high satellite velocities can be used to perform relativistic quantum information experiments, such as entanglement tests in the presence of special\index{Special relativity} and general relativity\index{General relativity}, Wheeler's delayed choice experiment\index{Wheeler's delayed choice experiment}, and enhanced quantum metrology \cite{bib:kaltenbaek2003proof, bib:scheidl2013quantum, bib:ahmadi2014relativistic}.

@@

Examples of how this type of model might be applied could include, but not be limited to research into:
\begin{itemize}
	\item Quantum information processing protocols, beyond only quantum computation, bits and qubits.
	\item Bose-Einstein condensates (BECs)\index{Bose-Einstein condensates (BECs)}.
	\item Light-matter interactions.\index{Light-matter interactions}
	\item Quantum thermodynamics and quantum statistical mechanics.\index{Quantum thermodynamics}\index{Quantum statistical mechanics}
	\item Quantum phase-transitions.\index{Quantum phase-transitions}
	\item Quantum optics, involving all manner of quantum states of light, beyond only those raised in Sec.~\ref{sec:opt_enc_of_qi}.\index{Quantum optics}
	\item Optical interferometry.\index{Optical interferometry}
	\item Providing a practical platform for university teaching and education.
\end{itemize}

In some instances, such outsourced quantum protocols might be applicable to encryption protocols, like those discussed in the next section (Sec.~\ref{sec:homo_blind}), enabling highly valuable secrecy for the experiments being conducted by researchers and their hard-earned results and ideas\footnote{Note, however, that the upcoming protocols are designed for application to particular optical states and protocols, and encryption schemes involving more generic quantum assets are likely to require some rethinking and adaptation (if possible at all, which isn't guaranteed!).}.

### 2018-10-18 Sections/encrypted_cloud_quantum_computing.tex
try101
Minor, refs

\dropcap{E}{xtremely} important to many high-performance data-processing applications is security, as proprietary or sensitive data may be being dealt with. To address this, there are two models for encrypted, outsourced quantum computation -- \textit{homomorphic encryption} \cite{???, gentry2009fully, van2010fully}\index{Homomorphic encryption} and \textit{blind quantum computation}\index{Blind quantum computation} \cite{???, bib:blind2, bib:blind3, bib:blind1, PhysRevLett.108.200502, bib:Morimae3486, bib:Morimae5460, bib:Morimae3966}.

>>>>

\dropcap{E}{xtremely} important to many high-performance data-processing applications is security, as proprietary or sensitive data may be being dealt with. To address this, there are two models for encrypted, outsourced quantum computation -- \textit{homomorphic encryption} \cite{bib:gentry2009fully, bib:van2010fully}\index{Homomorphic encryption} and \textit{blind quantum computation}\index{Blind quantum computation} \cite{bib:blind2, bib:blind3, bib:blind1, bib:PhysRevLett.108.200502, bib:Morimae3486, bib:Morimae5460, bib:Morimae3966}.
